### 2019-11-20 ch7_incgraph/content.tex
fix typo

Graphlets~ \cite{przulj_modelinginteractomescalefree_2004} are one of the tools which could be used to add a topological prior to a biological network,
Graphlets are small connected subnetworks which can be counted to identify which low-level topological patterns are present in a network. By comparing how topologically similar a predicted network is to what would be expected of a true biological network, a predicted network can be optimised in order to obtain a better topology.

>>>>

Graphlets~ \cite{przulj_modelinginteractomescalefree_2004} are one of the tools which could be used to add a topological prior to a biological network.
Graphlets are small connected subnetworks which can be counted to identify which low-level topological patterns are present in a network. By comparing how topologically similar a predicted network is to what would be expected of a true biological network, a predicted network can be optimised in order to obtain a better topology.
